\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards \vspace{-2ex} \versionline{11}

### 2015-09-15 ICRA2016/bandits_docs/includes/problem_statement.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

We consider the robust grasp planning problem for a single 3D object model and parallel-jaw grippers using probability force closure, $P_F$,  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
We assume the object shape is provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within. 
The object is specified in units of meters with given center of mass $\bz \in \mathbb{R}^3$.
We assume soft-finger contacts with a Coulomb friction model~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
%and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.

\subsection{Grasp and Object Parameterization}
\seclabel{grasp-param}
Our grasp parameterization is illustrated in~\figref{grasp-model}.
Let $\bg = (\bx, \bv)$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
%Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object for SDF $f$, and specify all points with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
Let $\mG = \{ (\bx, \bv) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mA\}$ denote the space of all objects, where $\mA$ is the space of all SDFs for closed and compact surfaces.
We denote by $\mM = \mG \times \mH$ the joint space of all parallel-jaw grasps and objects, also known as a Grasp Moduli Space~\cite{pokorny2013grasp}.

@@

\subsection{Sources of Uncertainty}
\seclabel{uncertainty}
We assume Gaussian distributions on object pose, gripper pose, and friction coefficient.
Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$.
Let $\nu \sim \mN\left(\mu_{\nu}, \Sigma_{\nu}\right)$ denote a Gaussian distribution on gripper pose with mean $\mu_{\nu} \in \mG$.
Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$ samples of object pose, gripper pose, and friction coefficient, respectively. 
%Theses sources of uncertainty might be estimated based on prior models of repeatability in gripper actuation or from the posterior variance in object pose or friction coefficient in estimates based on sensor data.

\subsection{Contact Model}
\seclabel{contact}
%Our contact model is illustrated in the right panel .
Given a grasp $\bg$ on an object $\mO$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface as shown in \figref{grasp-model}.
Each contact $\bc_i = \bx + (-1)^{i} (t_i^* - w / 2) \bv$ where~\cite{mahler2015gp}:
%\vspace{-1ex}
\begin{align*}
	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx +  (-1)^{i} (t - w / 2) \bv\right) = 0.
\end{align*}
\noindent Let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tangent vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
To compute the forces that each contact can apply to the object for friction coefficient $\hat{\gamma}$, we discretize the friction cone at $\bc_i$~\cite{pokorny2013c} into a set of $l$ facets with vertices $\mF_{i} = \left\{ \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \big| j = 1, ..., l \right\}$.
Each force $\bbf_{i,j} \in \mF_{i}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at $\bc_i$.
Under our soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
Thus the set of all contact wrenches that can be applied by a grasp $\bg$ under our model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.

\subsection{Quality Metric}
\seclabel{quality}
In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{mahler2015gp}, as our quality metric.
$P_F$ has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.

Let $F \in \{0, 1\}$ denote the occurrence of force closure.
Then for a grasp $\bg$ on object $\mO$, $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$~\cite{weisz2012pose}.

\subsection{Objective}
We are interested in finding $\bg^*$, the grasp that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net to reduce the samples needed to converge to $\bg^*$.

>>>>

We consider the robust grasp planning problem for a single 3D object model and parallel-jaw grippers using probability force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
We assume the object shape is provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within. 
The object is specified in units of meters with given center of mass $\bz \in \mathbb{R}^3$.
We assume soft-finger contacts with a Coulomb friction model~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
%and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.

\subsection{Grasp and Object Parameterization}
\seclabel{grasp-param}
The grasp parameters are illustrated in~\figref{grasp-model}.
Let $\bg = (\bx, \bv)$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
%Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object for SDF $f$, and specify all points with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
Let $\mG = \{ (\bx, \bv) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mA\}$ denote the space of all objects, where $\mA$ is the space of all SDFs for closed and compact surfaces.
We denote by $\mM = \mG \times \mH$ the Grasp Moduli Space of all parallel-jaw grasps and objects~\cite{pokorny2013grasp}.

@@

\subsection{Sources of Uncertainty}
\seclabel{uncertainty}
We assume Gaussian distributions on object pose, gripper pose, and friction coefficient to model errors in registration, robot calibration, or classification material properties, respectively.  
Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$.
Let $\nu \sim \mN\left(\mu_{\nu}, \Sigma_{\nu}\right)$ denote a Gaussian distribution on gripper pose with mean $\mu_{\nu} \in \mG$.
Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$ samples of the random variables.

\subsection{Contact Model}
\seclabel{contact}
Given a grasp $\bg$ on an object $\mO$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface as shown in \figref{grasp-model}.
Each contact $\bc_i = \bx + (-1)^{i} (w / 2 - t_i^*) \bv$ where~\cite{mahler2015gp}:
%\vspace{-1ex}
\begin{align*}
	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx +  (-1)^{i} (w / 2 - t) \bv\right) = 0.
\end{align*}
\noindent Let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tangent vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
To compute the forces that each contact can apply to the object for friction coefficient $\hat{\gamma}$, we discretize the friction cone at $\bc_i$~\cite{pokorny2013c} into a set of $l$ facets with vertices $\mF_{i} = \left\{ \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \big| j = 1, ..., l \right\}$.
Each force $\bbf_{i,j} \in \mF_{i}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at $\bc_i$.
Under the soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
Thus the set of all contact wrenches that can be applied by a grasp $\bg$ under the model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.

\subsection{Quality Metric}
\seclabel{quality}
In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{mahler2015gp}, as the quality metric.
$P_F$ has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.

Let $F \in \{0, 1\}$ denote the occurrence of force closure.
Then for a grasp $\bg$ on object $\mO$, $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
Then $F = 1$ if $\mathbf{0} \in Conv(\mW)$, where $Conv(\cdot)$ denotes the convex hull~\cite{weisz2012pose}.

\subsection{Objective}
We are interested in finding $\bg^*$, a grasp that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.

### 2015-09-15 ICRA2016/bandits_docs/includes/related_work.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

Robust grasp planning considers the problem of finding a set of grasps for an object that may succeed over perturbations in object shape,  object pose, and environment configurations due to uncertainty resulting from imprecision in perception and control.
Research on grasp planning for precisely known objects and environments has largely focused on finding grasps by maximizing an analytic grasp quality metric based on a Wrench Space (WS)~\cite{pokorny2013c}.
The need to recompute WS metrics for every new 3D object and grasp motivated research on grasp planning by transferring grasps from similar 3D objects in a database of prior knowledge~\cite{bohg2014data}.
To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated in GraspIt!.
%, and matched robot sensor data to synthetic depth maps of objects in the database using Iterated Closest Point to retrieve precomputed grasps for execution on a physical robot~\cite{goldfeder2011data}.
This led to research on methods for transferring grasps from objects in databases, such as warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.

Recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic WS metrics.
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by $P_F$ on 100 objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine, and achieved 80\% success in grasping objects on a table.

Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps decided by humans~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
In comparison, we learn a model predictive model of $P_F$ for parallel-jaw grasps on a new object based on similarity to prior 3D objects and grasps, and use our model for robust grasp planning with Multi-Armed Bandits (MAB).

Our work is also closely related to research on actively sampling grasps to build a statistical model of grasp quality from fewer examples~\cite{detry2011learning, kroemer2010combining, salganicoff1996active}.
%Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
%Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
%Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Oberlin and Tellex~\cite{oberlin2015autonomously} developed a confidence-bound based MAB algorithm for planning parallel-jaw grasps using prior information on short time horizons, but do not study the effects of orders of magnitude of prior data on convergence.
Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high $P_F$.

>>>>

Grasp planning considers the problem of finding grasps for a given object that achieve force closure or optimize a related quality metric~\cite{pokorny2013c}.
Usually it is assumed that the object is known exactly and that contacts are placed exactly, and mechanical wrench space analysis is applied.
Robust grasp planning considers the same problem in the presence of bounded perturbations in properties such as object shape, pose, or mechanical properties such as friction, which are inevitable due to imprecision in perception and control.
One way to treat perturbations is statistical sampling.
Since sampling in high dimensions can be computationally demanding, recent work has explored how a robust grasps computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the GraspIt! stochastic sampling-based grasp planner.
%This led to research on methods for transferring grasps from objects in databases, such as warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.

Recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic WS metrics.
Brook et al.~\cite{brook2011collaborative} planned robust grasps for a database of 892 point clouds and developed a model to predict grasp success on a physical robot based on correlations with grasps in the database.   
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by $P_F$ on 100 objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine, and achieved 80\% success in grasping objects on a table.

Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps from human demonstrators~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
We estimate $P_F$ using similar objects and grasps using a variant of the Multi-Armed Bandit (MAB) model for sequential decision-making.

Our work is also closely related to research on actively sampling grasps to build a statistical model of grasp quality from fewer examples~\cite{detry2011learning, kroemer2010combining, salganicoff1996active}.
%Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
%Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
%Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Oberlin and Tellex~\cite{oberlin2015autonomously} developed a budgeted MAB algorithm for planning 3 DOF crane grasps a using priors from the responses of hand-designed depth image filters, but did not study the effects of orders of magnitude of prior data on convergence.
Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high $P_F$.

### 2015-09-15 ICRA2016/bandits_docs/paper.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

%\benkhide

@@

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and a Multi-Armed Bandit Model with Correlated Rewards to Accelerate Robust Grasp Planning
	%\vspace{-2ex}
	\versionline{9}}
\author{Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,2}$, \\
Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^{1}$
%\vspace{-2ex}
\thanks{{\small $^1$ University of California, Berkeley, USA; {\tt\small \{jmahler, ftpokorny, brian.hou, goldberg\}@berkeley.edu, melrose\_roderick@brown.edu}}}%
%\thanks{$^2$IEOR Dept; {\tt\small goldberg@berkeley.edu}}%
%\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{{\small $^2$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}}%
\thanks{{\small $^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}} }
}
\maketitle

%\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
%\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
\TODO{Trim paper to 8 pages}
\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/dataset}
%\input{includes/background}
\input{includes/algorithm}
\input{includes/experiments}
\input{includes/conclusion}

>>>>

\benkhide

@@

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards
	\vspace{-2ex}
	\versionline{11}}
\author{Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,2}$, \\
Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^{1}$
%\vspace{-2ex}
\thanks{{\small $^1$ University of California, Berkeley, USA; {\tt\small \{jmahler, ftpokorny, brian.hou, goldberg\}@berkeley.edu, melrose\_roderick@brown.edu}}}%
%\thanks{$^2$IEOR Dept; {\tt\small goldberg@berkeley.edu}}%
%\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{{\small $^2$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}}%
\thanks{{\small $^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}} }
}
\maketitle

%\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
%\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
%\TODO{Trim paper to 8 pages}
\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/dataset}
%\input{includes/background}
\input{includes/algorithm}
\input{includes/experiments}
\input{includes/conclusion}
